experiment 1

### 2021-11-11 experiments/experiment 1/experiment-1.Rmd
Update experiment-1.Rmd

## num_div_treatment_levels <- 20

num_div_treatment_levels <- 3 ## FOR TEST

@@

```{r}
display_diversity(
  9, ## FOR TEST was 400
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

@@

### Maximum diversity

```{r eval = eval_dynamics_flag}
# Is this actually needed?
# sim_number <- num_div_treatment_levels

parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

### Maximum diversity

```{r eval = eval_dynamics_flag}
sim_number <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

### Medium diversity

```{r eval = eval_dynamics_flag}
try_me <- 311
sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

>>>>

num_div_treatment_levels <- 20

## num_div_treatment_levels <- 3 ## FOR TEST

@@

```{r}
display_diversity(
  400,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

@@

### With diversity

```{r eval = eval_dynamics_flag}
# Is this actually needed?
# sim_number <- num_div_treatment_levels
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar1$strain_parameter$initial_state
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/experiment 1/data/sim_res_highvar1.RDS"))
```

@@

### With diversity

```{r eval = eval_dynamics_flag}
#sim_number <- num_div_treatment_levels
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
#parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar2$strain_parameter$initial_state
sim_res_highvar2 <- run_simulation(parameter)
saveRDS(sim_res_highvar2, here("experiments/experiment 1/data/sim_res_highvar2.RDS"))
```

@@

### With diversity

```{r eval = eval_dynamics_flag}
try_me <- 311
#sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```
